### 2019-12-21 defesa/tex/chapter/introducao.tex
wip

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
In this first study, the author defined the problem for graphs, such that the demand set is a subset of the graph's vertices. Given a facility set where each facility has a coverage radius, the problem asks to choose vertices to place the facilities to maximize the coverage of the demand set.

>>>>

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.

In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices. Given a facility set where each facility has a coverage radius, the objective was then to maximize the coverage of the demand set by choosing vertices to place each facility.
